Optimal (Multiway) Spatial Joins

### 2024-05-29 msj.tex
yufei

\extraspacing {\bf Computing $\bm{R^*_1, R^*_2, ..., R^*_{k-2}}$.} We consider, w.l.o.g., that each rectangle $r$ in the input $R_1 \cup ... \cup R_{k-2}$ is given a distinct integer ID in $[n]$. This allows us to create an array $A$ of size $n$ and store in $A[i]$ ($i \in [n]$) a constant amount of information for each $r$.

>>>>

\input{4.2}

\extraspacing {\bf Computing $\bm{R^*_1, R^*_2, ..., R^*_{k-2}}$.} We consider, w.l.o.g., that each rectangle in the input $R_1 \cup ... \cup R_{k-2}$ is given a distinct integer ID in $[n]$. This allows us to create an array $A$ of size $n$ and allocate a cell of $A$ to each $r \in R_1 \cup ... \cup R_{k-2}$. The cell can be accessed by the ID of $r$ in constant time.
